---
title: "LabExer#3"
author: "Rey Angelo Calopez"
date: "2024-02-28"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
I'm using MySQL WorkBench
MY SQL DATABASE:

CREATE DATABASE dbreviews;

USE dbreviews;

CREATE TABLE reviews (
id INT PRIMARY KEY AUTO_INCREMENT,
movie_title TEXT,
reviewer_name TEXT,
review_date VARCHAR (30),
review_rating VARCHAR(30),
review_content TEXT,
review_title TEXT
);

PASSWORD: password
```{r}

#install.packages("dplyr")
#install.packages("rvest")
#install.packages("polite")
#install.packages("httr")

library(dplyr)
library(rvest)
library(polite)
library(httr)


reviews <- data.frame()

link <- "https://www.imdb.com/title/tt0111161/reviews?ref_=tt_urv"
session <- bow(link, user_agent = "Educational Purpose")

scrapeNodes <- function(selector) {
  scrape(session) %>%
    html_nodes(selector) %>%
    html_text(trim = TRUE)
}

titleMovie <- scrapeNodes("a.subnav_heading")
reviewer <- scrapeNodes("span.display-name-link")[1:10]
scrapedDate <- scrapeNodes("span.review-date")[1:10]
scrapedRating <- scrapeNodes("span.rating-other-user-rating")[1:10]
scrapedReview <- scrapeNodes("div.text.show-more__control")[1:10]
scrapedTitleReview <- scrapeNodes("a.title")[1:10]

reviews <- rbind(reviews, data.frame(
  movie_title = rep(titleMovie, 10),
  reviewer_name = reviewer,
  review_date = scrapedDate,
  review_rating = scrapedRating,
  review_content = scrapedReview,
  review_title = scrapedTitleReview
))

reviews

```

CREATING CONNECTIONS

```{r}

library(dplyr,dbplyr)
library(RMySQL)

#creating connections
connection <- dbConnect(RMySQL::MySQL(),
                        dsn="MariaDB-connection",
                        Server = "localhost",
                        dbname = "dbreviews", 
                        user = "root", 
                        password = "password") 

```

LISTING TABLES AND FIELDS

```{r}
dbListTables(connection)
dbListFields(connection,"reviews")
```

READING DATA FROM DATABASE

```{r}

review_data <- dbGetQuery(connection, "SELECT * FROM dbreviews.reviews")

glimpse(review_data)

```

INSERTING REVIEWS TO DATABASE

```{r}

#use the gsub function to replace all single quotes in the review_content and review_title columns with two single quotes (''). 
#This will ensure that any single quotes in the text are properly escaped in the SQL query.

for (i in 1:nrow(reviews)) {
    query <- paste0("INSERT INTO reviews (movie_title, reviewer_name, review_date, review_rating, review_content, review_title) 
                  VALUES ('", reviews$movie_title[i],"','", reviews$reviewer_name[i], "','", reviews$review_date[i],"','", reviews$review_rating[i], "','",
                  gsub("'","''", reviews$review_content[i]), "','", gsub("'","''", reviews$review_title[i]), "')")
  
  #execute query
  query_result <- dbSendQuery(connection, query)
  
  #clear result after executing query
  dbClearResult(query_result)
}

```

READ AND VIEW INSERTED DATA

```{r}

review_data <- dbGetQuery(connection, "SELECT * FROM dbreviews.reviews")


# VIEW REVIEWS without primary key "id"
review_data[,c(2:7)]

#View(review_data[,c(2:7)])

#Export to csv
write.csv(review_data[,c(2:7)], "review_data.csv")

```

```{r}
# Close the database connection
dbDisconnect(connection)

```